### 2016-05-26 syntax.tex
hammering on syntax

\section{Syntax}
\tsnote{Very much a work-in-progress.}
As a first step, let us try to better formalize Bloom filters as a primitive.

@@

@@

>>>>

\section{Syntax}
As a first step, let us try to better formalize Bloom filters as a primitive.

@@

\tsnote{Very much a work-in-progress.}

@@

\tsnote{Below is an alternative way to formalize things like counting Bloom filters, count-min sketch, scaling Bloom filters, etc.  Neither is solid, yet.}
